Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-10 mtjournal.tex
added corpus introduction to F/A section

\section{Correlation with human judgments of fluency \& adequacy}
\label{sec:faexpts}
Corpus: LDC Multiple Translation Chinese corpus 3\&4 treat each
segment and each judgment as independent data point

\begin{itemize}
\item EXPT

  using n=1 parse for DPM variants

@@

\item EXPT

  combining precision, recall naively vs. combining items

@@

\item  EXPT

  setting gamma

>>>>

\section{Correlation with human judgments of fluency \& adequacy}
\label{sec:faexpts}

TO DO: INTRODUCE THIS SECTION

\subsection{Corpus}

For these experiments, we use LDC Multiple Translation Chinese corpus
parts 2~\cite{LDC03MTC2} and 4~\cite{LDC06MTC4}.  These corpora
include multiple human judgments of fluency and adequacy for each
sentence, with each judgment using a different human judge and a
different reference translation.  For a rough\footnote{Our segment
  count differs from \cite{owczarzak07labelleddepseval}, who report
  16,800 segments over the same corpus. We find baseline correlations
  (BLEU$_4$ and TER) lower than those reported there as well, so the
  results presented here are not directly comparable with that paper,
  though we demonstrate similar gains over those baselines in
  essentially the same corpus. % (section~\ref{sec:facorr:newdeps}).}
}
comparison with \cite{owczarzak07labelleddepseval}, we treat each
judgment as a separate segment.
%
This treatment of this corpus yields 16,815 tuples of
$\langle$hypothesis, reference, fluency, adequacy$\rangle$.  In these
experiments, we extend this tuple with automatic scores derived from
$\langle$hypothesis, reference$\rangle$ and examine the
correlations\footnote{The independence of each of these segments is
  questionable, since the same hypothesis translations are used in
  multiple items, but for the sake of methodological comparison with
  prior work, this strategy is preserved.}  between those automatic
scores and the arithmetic mean of the fluency and adequacy measures.

\begin{itemize}
\item EXPT  using n=1 parse for DPM variants

@@

\item EXPT 
  combining precision, recall naively vs. combining items

@@

\item  EXPT
  setting gamma
